supplementary figures

### 2019-11-11 PaperFigures.Rmd
re-ordered TH groups

a<-baseplot(melt[melt$variable=="TNFα",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,1500))+
    labs(y="pg/mL")
b<-baseplot(melt[melt$variable=="IFNγ",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,18000))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
c<-baseplot(melt[melt$variable=="IL-21",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,60))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
d<-baseplot(melt[melt$variable=="IL-17A",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,20))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
e<-baseplot(melt[melt$variable=="IL-22",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,40))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
f<-baseplot(melt[melt$variable=="IL-10",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,20))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
g<-baseplot(melt[melt$variable=="IL-4",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,40))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
h<-baseplot(melt[melt$variable=="IL-5",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,15))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))
i<-baseplot(melt[melt$variable=="IL-13",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,400))+
    theme(plot.margin=margin(l=-0.5,unit="cm"))

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1/figures")
cowplot::save_plot("figure8.png", lumplot, base_height=6, base_width=18)

>>>>

a<-baseplot(melt[melt$variable=="TNFα",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,1500))+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    labs(y="pg/mL")
b<-baseplot(melt[melt$variable=="IFNγ",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,18000))
c<-baseplot(melt[melt$variable=="IL-21",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,60))
d<-baseplot(melt[melt$variable=="IL-17A",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,20))
e<-baseplot(melt[melt$variable=="IL-22",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,40))
f<-baseplot(melt[melt$variable=="IL-10",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,20))
g<-baseplot(melt[melt$variable=="IL-4",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,40))
h<-baseplot(melt[melt$variable=="IL-5",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,15))
i<-baseplot(melt[melt$variable=="IL-13",], "SM", "value", ltbi.cols)+facet_wrap(~variable)+
    theme(plot.margin = unit(c(0,0,0,0), "cm"))+
    coord_cartesian(ylim=c(0,400))

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Mtb Manuscript/figures")
cowplot::save_plot("figure8.png", lumplot, base_height=5, base_width=18)

### 2019-11-11 SuppFigures.Rmd
re-ordered TH groups

th1.2<-booleanplot2(test[test$th=="TH1/2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())+
    labs(y="(%) CD4 T cells")

th1<-booleanplot2(test[test$th=="TH1",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,25))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())

th2<-booleanplot2(test[test$th=="TH2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))
```

```{r, fig.height=10, fig.width=10}
supp2<-cowplot::plot_grid(th1.2, th1, th2, ncol=3, rel_widths = c(8,3.5,3.5))
supp2
```

@@

a<-booleanplot2(test, "variable", "value", all.cols)+facet_grid(~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, exact=FALSE, size=10)+
    coord_cartesian(ylim=c(0,.16))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) CD4 T cells")

@@

a<-booleanplot2(test, "variable", "value", all.cols)+facet_grid(~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, exact=FALSE, size=10)+
    coord_cartesian(ylim=c(0,.16))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) CD4 T cells")

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1")
cowplot::save_plot("supp2.png", supp2, base_height=8, base_width=10)
cowplot::save_plot("supp3.png", supp3, base_height=14, base_width=10)
cowplot::save_plot("supp4.png", supp4, base_height=12, base_width=12)
cowplot::save_plot("supp5.png", supp5, base_height=15, base_width=16)
cowplot::save_plot("supp6.png", supp6, base_height=12, base_width=12)
cowplot::save_plot("supp7.png", supp7, base_height=15, base_width=16)
cowplot::save_plot("supp8.png", supp8, base_height=14, base_width=16)
cowplot::save_plot("supp9.png", supp9, base_height=14, base_width=16)
cowplot::save_plot("supp10.png", supp10, base_height=15, base_width=16)
```

>>>>

th1<-booleanplot2(test[test$th=="TH1",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,25))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())+
    labs(y="(%) CD4 T cells")

th1.2<-booleanplot2(test[test$th=="TH1/2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,3))+
    theme(strip.text.y = element_blank(), strip.background.y = element_blank())

th2<-booleanplot2(test[test$th=="TH2",], "variable", "value", all.cols)+facet_grid(TB~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10, label.y = 20)+
    coord_cartesian(ylim=c(0,1.5))
```

```{r, fig.height=10, fig.width=10}
supp2<-cowplot::plot_grid(th1, th1.2, th2, ncol=3, rel_widths = c(3,8,3.5))
supp2
```

@@

test$th<-"TH1/2"
test$th[grep("._x_x_.", test$variable)]<-"TH1"
test$th[grep("x_._._x|x_._.._x", test$variable)]<-"TH2"
test$th<-factor(test$th, levels=c("TH1", "TH1/2", "TH2"))

a<-booleanplot2(test, "variable", "value", all.cols)+facet_grid(~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", 
                       hide.ns = TRUE, exact=FALSE, size=10, label.y=(.98*.12))+
    coord_cartesian(ylim=c(0,.12))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) CD4 T cells")

@@

test$th<-"TH1/2"
test$th[grep("._x_x_.", test$variable)]<-"TH1"
test$th[grep("x_._._x|x_._.._x", test$variable)]<-"TH2"
test$th<-factor(test$th, levels=c("TH1", "TH1/2", "TH2"))

a<-booleanplot2(test, "variable", "value", all.cols)+facet_grid(~th, scales="free", space="free")+
    scale_x_discrete(labels = cyt_labels, breaks=cyt_breaks)+
    stat_compare_means(method="wilcox.test", label="p.signif", 
                       hide.ns = TRUE, exact=FALSE, size=10, label.y=(.98*0.11))+
    coord_cartesian(ylim=c(0,.11))+
    theme(plot.margin=margin(l=1,unit="cm"))+
    labs(y="(%) CD4 T cells")

@@

#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Mtb Manuscript/")
cowplot::save_plot("supp2.png", supp2, base_height=8, base_width=10)
cowplot::save_plot("supp3.png", supp3, base_height=14, base_width=10)
cowplot::save_plot("supp4.png", supp4, base_height=12, base_width=12)
cowplot::save_plot("supp5.png", supp5, base_height=15, base_width=16)
cowplot::save_plot("supp6.png", supp6, base_height=12, base_width=12)
cowplot::save_plot("supp7.png", supp7, base_height=15, base_width=16)
cowplot::save_plot("supp8.png", supp8, base_height=14, base_width=16)
cowplot::save_plot("supp9.png", supp9, base_height=14, base_width=16)
cowplot::save_plot("supp10.png", supp10, base_height=15, base_width=16)
```
